Solution-aware vs global ReLU selection: \\ partial MILP strikes back for DNN verification

### 2025-04-23 ATVA 2025/proofsb.tex
update table
update
update plot

@@

\textcolor{red}{Direct MILP encodings are inefficient! Even the advanced Gurobi MILP solver struggle to sort out all neurons – see Fig11 page27: direct MILP encoding is $>10$ times slower on same instance ($>300s$ vs $<30s$ for similar accuracy) wrt considering only 8 open nodes selected with SAS (more open nodes lead to larger differences). Our main contribution is a way to select the most important nodes, and it helps Gurobi tremendously. This is the whole point of the paper!}

>>>>

\begin{table}
	\begin{tabular}{|c|c|c|c|c|}
		\hline
		NodeID & $\UB$ by SAS& Time cost & $\UB$ by GS  & Time cost \\
		\hline
	0 & -1.4684063 & 66.9 & -1.3804709 & 71.6 \\
	\hline
	2 & -4.5550154 & 54.8 & -4.5424599 & 84.9 \\
	\hline
	3 & -4.4795618 & 69.9 & -4.4459532 & 71.2 \\
	\hline
	4 & -3.4594076 & 88.8 & -3.4784499 & 113 \\
	\hline
	5 & -5.5981178 & 94.8 & -5.6955818 & 93.7 \\
	\hline
	6 & -3.0597499 & 63.3 & -2.9797569 & 68.5 \\
	\hline
	7 & -4.1742691 & 73.4 & -4.0842553 & 88.6 \\
	\hline
	8 & 0.63875415 & 56.7 & 0.72631579 & 46.5 \\
	\hline
	9 & -2.3270878 & 64.6 & -2.2841141 & 69.4 \\
	\hline
		Average & -2.3270878 & 64.6 & -2.2841141 & 69.4 \\
	\hline
		Variant & -2.3270878 & 64.6 & -2.2841141 & 69.4 \\
	\hline
	\end{tabular}
	\vspace*{1ex}
	 \caption{Time cost and accuracy by SAS (open 30 nodes and 14 nodes) and GS (open 30 nodes). Here, smaller $\UB$ means higher accuracy and positive means verified.}
\end{table}

@@
